Dependent Object Types

### 2012-07-03 doc/semester/report.tex
slides up to all counterexs

Now, $f$ is a subtype of $\Top \tfun \Top$, but $\app f {(\abs x \Top
  x)}$ is stuck (and, rightfully, doesn't typecheck). But we can use
narrowing to create a counterexample to preservation: $\app {(\abs g
  {\Top \tfun \Top} {g (\abs x \Top x)})} f$.

@@

Even well-formedness is not preserved by narrowing. The trick is that
if the lower bound of a type selection is not $\Bot$, then the upper
bound needs to be checked for well-formedness. Here, we create two
type selections that are mutually recursive in their upper bounds
after narrowing. $y.A$ is initially well-formed, but after narrowing,
it isn't because we run into an infinite derivation trying to prove
the well-formedness of its upper bound.

>>>>

Now, $f$ is a subtype of $\Top \tfun \Top$, but $\app f {(\abs x \Top
  x)}$ is stuck (and, rightfully, doesn't typecheck). But we can use
narrowing to create a counterexample to preservation: $\app {(\abs g
  {\Top \tfun \Top} {\app g (\abs x \Top x)})} f$.

@@

Even well-formedness is not preserved by narrowing. The trick is that
if the lower bound of a type selection is not $\Bot$, then the
bounds needs to be checked for well-formedness. Here, we create two
type selections that are mutually recursive in their bounds
after narrowing. $y.A$ is initially well-formed, but after narrowing,
it isn't because we run into an infinite derivation trying to prove
the well-formedness of its bounds.
